\documentclass[../ProjectFoundation.tex]{subfiles}

\begin{document}
\textbf{General:}
\begin{enumerate}
	\item Everyone should be on time. Rather 5 minutes too early than 5 minutes late.
	\item Project work days are usually Fridays, but if necessary more days will be scheduled.
	\item If a group member is running late they are required to inform another group member either by Facebook or mobile.
	\item If a group member cannot attend the scheduled project workday, they are required to give notice asap.
\	item Every third time a group member is more than 5 minutes late, they must bring cake for the group, the next project workday.
\end{enumerate}
\textbf{Preparation:}
\begin{enumerate}
	\item The work material to be prepared before a project workday is agreed upon on the previous project workday. (In special cases, Facebook can be used to coordinate work material).
	\item Group members are required to complete any task given to them, by the agreed upon deadline.
	\item Group members needing help with their task should make sure to seek help from other members as soon as possible.
\end{enumerate}
\textbf{Agreement:}
\begin{enumerate}
	\item All decisions are decided by simple majority.
	\item If the group members cannot find agreement, they will seek the help of their adviser.
	\item The project will be written partly in Google docs and \LaTeX{}.
\end{enumerate}
\textbf{Teambuilding:}
\begin{enumerate}
	\item The work pace should not be grueling, as there should be time to have fun and team build. That said, the work should be completed within the deadlines.
	\item If a group member is working and you?re taking a break, it is expected that you don?t do anything to break their concentration. (Loud off topic discussions, music etc.)
	\item Breaks can be coordinated within the group, or short breaks can be taken individually.
\end{enumerate}
\textbf{Level of ambition:}
\begin{enumerate}
	\item It is expected that every group member?s ambition level should be high.
	\item The ambition level can under special circumstances (deadlines, etc.) be changed, as long as the group agrees.
\end{enumerate}
\textbf{Learning:}
\begin{enumerate}
	\item It is up to the individual group member to take responsibility for his/her own learning.
\end{enumerate}
\textbf{Work Culture:}
\begin{enumerate}
	\item Group members should be respectful of each other. (Let them speak and listen to their points of view)
	\item If a problem should occur between group members (academically or personally), it should be addressed as soon as possible.
	\item Work problems should be solved by groups of two where possible.
	\item The work tasks of the day should be clear and thought out beforehand.
	\item At the end of the project workday, the results should be evaluated and the work tasks for next time should be planned.
	\item In case of serious violation of the cooperation agreements, the advisor will be contacted.
	\item It is expected that every group member attends lectures and actively seeks to further their understanding of Software Engineering, to help the group succeed.
\end{enumerate}

\end{document}
