\documentclass[11pt]{article}
%Relevante pakker
\usepackage{enumerate}
\usepackage{tabularx}
\usepackage[table]{xcolor}
%Irelevante pakker
\usepackage{parskip}
\usepackage[margin=1in,includefoot]{geometry}

\begin{document}
\section*{Requirements}
\subsection*{Functional Requirements}
\begin{enumerate}[F01]
	\item Protagonist and NPC's\footnote{Non Playable Character} can move.
	\item Protagonist can aim in any direction.
	\item Protagonist can collect items from the ground.
	\item Protagonist can equip collected items.
	\item Protagonist can consume potions.
	\item Protagonist can gain experience points to gain levels.
	\item Protagonist can spend levelpoints to increase stats (attributes eg. strength, fire rate, and precision).
	\item Protagonist can purchase potions (power-ups)
	\item Protagonist and NPC's can fire their weapon
	\item Protagonist and NPC's can take damage.
	\item Protagonist and NPC's will die, if damage exceeds their hit points (HP).
	\item Hostile NPC's has a chance to drop loot, when they die.

\end{enumerate}
\subsection*{Non-Functional Requirements}
\subsubsection*{Product requirements}
\begin{enumerate}[P01]
	\item The system must save select game data to a database.
	\item The system should be developed using JMonkeyEngine (JME).
	\item The system should be developed in Java SE.
	\item The system should be compatible with Windows, Mac OS X and Linux.
 	\item The system must be component based, and implement a component framework.
 	\item Components must be able to load and unload dynamically.
 	\item The system must apply algorithms and data-structures.
	\item The system must implement an AI.
\end{enumerate}
\subsubsection*{Quality requirements}
\begin{enumerate}[Q01]
	\item The game world should be procedurally generated.
	\item The game should be playable with a game controller.
	\item Equip-able items should be randomly generated.
	\item The game should contain an engaging soundtrack.
	\item The game must detect collisions between entities.
	\item NPC's must implement an AI
\end{enumerate}
\subsubsection*{Supplementing requirements}
\begin{enumerate}[S01]
	\item Hello

\end{enumerate}

\subsection*{Requirement Prioritization\\[.2cm]}
\begin{tabularx}{\textwidth}{|c|X||c||c|c|c||c|}

	\hline \multicolumn{7}{|c|}{\cellcolor{gray!50}\textbf{Functional Requirements}} \\\hline
 	Id  & Name & MoSCoW & Sys.\footnote{System benefit} & Arch.\footnote{Architectural importance} & Risk & Total\\\hline
 	F09 & Protagonist and NPC's can use their weapon & $M$ & $5$ & $3$ & $2$ & $10$ \\\hline
 	F01 & Protagonist and NPC's can move. & $M$ & $4$ & $1$ & $2$ & $7$ \\\hline
 	F02 & Protagonist can aim in any direction. & $M$ & $4$ & $1$ & $2$ & $7$ \\\hline\hline
 	F11 & Protagonist and NPC's will die, if damage exceeds their HP. & $S$ & $3$ & $3$ & $3$ & $9$ \\\hline
 	F10 & Protagonist and NPC's can take damage. & $S$ & $3$ & $1$ & $2$ & $6$ \\\hline\hline
 	F04 & Protagonist can equip collected items. & $C$ & $3$ & $3$ & $3$ & $9$ \\\hline
 	F12 & Hostile NPC's has a chance to drop loot, when they die. & $C$ & $3$ & $2$ & $3$ & $8$ \\\hline
 	F03 & Protagonist can collect items from the ground. & $C$ & $3$ & $2$ & $2$ & $7$ \\\hline
 	F05 & Protagonist can consume potions & $C$ & $3$ & $2$ & $2$ & $7$ \\\hline
 	F06 & Protagonist can gain experience points. & $C$ & $1$ & $1$ & $2$ & $4$ \\\hline\hline
 	F07 & Protagonist can purchase potions & $W$ & $1$ & $1$ & $1$ & $3$ \\\hline
 	F08 & Protagonist can spend level-points to increase stats & $W$ & $1$ & $1$ & $1$ & $3$ \\\hline

\end{tabularx}

\begin{tabularx}{\textwidth}{|c|X||c||c|c|c||c|}
	\hline\multicolumn{7}{|c|}{\cellcolor{gray!50}\textbf{Non-Functional Requirements}} \\\hline
 	Id  & Name & MoSCoW & Sys. & Arch. & Risk & Total\\\hline
	\multicolumn{7}{|c|}{\cellcolor{gray!25}Product Requirements} \\\hline
 	P02 & The system must be developed using JMonkeyEngine (JME). & $M$ & $-$ & $-$ & $-$ & $-$ \\\hline
 	P03 & The system must be developed in Java SE. & $M$ & $-$ & $-$ & $-$ & $-$ \\\hline
 	P05 & The system must be component based. & $M$ & $-$ & $-$ & $-$ & $-$ \\\hline
 	P06 & Components must be able to load and unload dynamically. & $M$ &  $-$ & $-$ & $-$ & $-$ \\\hline
 	P07 & The system must apply algorithms and data-structures. & $M$ &  $-$ & $-$ & $-$ & $-$ \\\hline
 	P08 & The system must implement an AI. & $M$ &  $-$ & $-$ & $-$ & $-$ \\\hline\hline
 	P01 & The system should save select game data to a database. & $S$ & $4$ & $3$ & $3$ & $10$ \\\hline
  	P04 & The system should be compatible with Windows, Mac OS X and Linux. & $S$ & $-$ & $-$ & $-$ & $-$ \\\hline
 	
	\multicolumn{7}{|c|}{\cellcolor{gray!25}Quality Requirements} \\\hline
	
 	Q05 & The game must detect collisions between entities. & $M$ & $5$ & $4$ & $5$ & $14$ \\\hline\hline
 	Q01 & The game world should be procedurally generated. & $S$ & $4$ & $4$ & $4$ & $12$ \\\hline\hline
 	Q04 & The game could contain an engaging soundtrack. & $C$ & $1$ & $2$ & $2$ & $5$ \\\hline
 	Q02 & The game should be playable with a game controller. & $C$ & $2$ & $1$ & $1$ & $4$ \\\hline
 	Q03 & Equip-able items should be randomly generated. & $C$ & $2$ & $1$ & $1$ & $4$ \\\hline
	
	\multicolumn{7}{|c|}{\cellcolor{gray!25}Supplementing Requirements} \\\hline
 	S01 & Hello & $x$ & $x$ & $x$ & $x$ & $3x$ \\\hline
	
\end{tabularx}


\end{document}
